Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-10-14 crowdsource/article.tex
Remove conflicts symbols but keep both alternatives

The inference problem reduced to its simpliest shape is the identification of
neuron pairs that are directly connected in the network. Intuitively, such
pairs should be related somehow and in particular their activities have to be
similar since their are dependent on the connectivity network. Therefore a way
to identify them is to measure, or at least estimate, how closely related two
neurons are regarding their activities. The most common measure for that
purpose is the (Pearson) correlation.  However, correlation also measures the
degree of association between neurons that are connected through others and so 
connected indirectly. It means all related neurons are found but direct pairs
are indinstinguishable from indirect ones.

@@

@@

>>>>

\paragraph{A first version}
The inference problem reduced to its simpliest shape is the identification of
neuron pairs that are directly connected in the network. Intuitively, such
pairs should be related somehow and in particular their activities have to be
similar since their are dependent on the connectivity network. Therefore a way
to identify them is to measure, or at least estimate, how closely related two
neurons are regarding their activities. The most common measure for that
purpose is the (Pearson) correlation.  However, correlation also measures the
degree of association between neurons that are connected through others and so 
connected indirectly. It means all related neurons are found but direct pairs
are indinstinguishable from indirect ones.

@@

\paragraph{Alternative}
A simple yet effective solution to the problem of connectome inference in
calcium imaging data consists of two steps. \cite{sutera2014simple} First,
processing the raw signals and to detect neural peak activities while filtering
noise. Second, inferring the degree of association between neurons from partial
correlation statistics, the inverse of the correlation matrix. This statitical
measure has the property to filter indirect associations between neuron and
gives a high degree of association between directly connected neurons. This
approach is the winning methods of the Connectomics challenge.

@@

As
